---
title: "Assignment 1"
---

My first assignment has two parts:

## (a)

Here is the video I have watched:[Veri Bilimi ve Endüstri Mühendisliği Üzerine Sohbetler - Mustafa Baydoğan & Erdi Daşdemir](https://www.youtube.com/watch?v=1Mvkn71dhaA&t)

The video is about Associate Professor Mustafa Gökçe Baydoğan conveying his experiences and knowledge about data science.

Mr. Baydoğan completed his undergraduate and graduate studies at Middle East Technical University and then went to Arizona State University in America to do his doctorate.After his PhD, he did some research and returned to Türkiye and is currently working here as a faculty member at Boğaziçi University.He is also the founder of Algopoly Software and Consulting A.Ş.

Mr. Baydoğan works on large-scale data mining, time series analysis, pattern discovery, operations research using data science tools.In this conversation, he also tells about his own sectoral experiences.

## **Questions**

**1)**The results that we have calculated theoretically and reached thanks to past experiences can sometimes be wrong.What is it called if a demand forecast is incorrect due to the fact that real-life data is dirty?

Answer:Censored Demand

**2)** Which of the following is not one of the decision-making processes in traditional/deep learning methods?

a)Interpretability

b)Ability to Direct

c)Ability to Reproduce

d)Being Able to Robust

e)Ability to Translate into a Decision

Answer:c

## (b)

In the second part of the assignment, I have completed some tasks:

• Import the “polls_us_election_2016” data set from the dslabs package.

```{r chunk_1}
library(dslabs)
data("polls_us_election_2016")
```

• Display the first 10 rows of the data set.

```{r chunk_2}
first_ten_row <- head(polls_us_election_2016,10)
print(first_ten_row)
```

• Calculate and display the total number of NA values in the entire data set.

```{r}
total_na <- sum(is.na(polls_us_election_2016))
total_na
```

• Replace all NA values in the “polls_us_election_2016” data set as follows: For numeric columns, replace NA values with your birth year. For character or factor columns, replace NA values with your first name. Store the modified data set as a new object.Print the first ten rows of the new data frame.

```{r}
birth_year <- 2002
first_name <- "Yazel"

no_nas_data <- polls_us_election_2016

for (col in names(no_nas_data)) { # Convert factor columns to character to prevent coercion issues.
  if (is.factor(no_nas_data[[col]])) {
    no_nas_data[[col]] <- as.character(no_nas_data[[col]])
  }
  # Check if the column is numeric.
  if (is.numeric(no_nas_data[[col]])) {
    # Replace NA values with the birth year.
    no_nas_data[[col]] <- ifelse(is.na(no_nas_data[[col]]), birth_year, no_nas_data[[col]])
    # Check if the column is character or already a character (after conversion).
  } else if (is.character(no_nas_data[[col]])) {
    # Replace NA values with the first name.
    no_nas_data[[col]] <- ifelse(is.na(no_nas_data[[col]]), first_name, no_nas_data[[col]])
  }
  # No need for an else statement since we do nothing for other column types
}

new_first_ten_row <- head(no_nas_data, 10)
new_first_ten_row

#[^1]
```

• Print the total number of NAs remaining in the new data frame.

```{r}
total_na<-sum(is.na(no_nas_data))
total_na
```

\[\^1\]:I wrote this code with the help of ChatGPT using that prompt:

Can you tell me how to change the NA values in the R Programming language according to the column types with the if command?
