---
title: "Assignment 1"
---

My first assignment has two parts:

## (a)

Here is the video I have watched:[Veri Bilimi ve Endüstri Mühendisliği Üzerine Sohbetler - Mustafa Baydoğan & Erdi Daşdemir](https://www.youtube.com/watch?v=1Mvkn71dhaA&t)

The video is about Associate Professor Mustafa Gökçe Baydoğan conveying his experiences and knowledge about data science.

Mr. Baydoğan completed his undergraduate and graduate studies at middle east technical university and then went to Arizona State University in America to do his doctorate.After his PhD, he did some research and returned to Türkiye and is currently working here as a faculty member at Boğaziçi University.He is also the founder of Algopoly Software and Consulting A.Ş.

Mr. Baydoğan works on large-scale data mining, time series analysis, pattern discovery, operations research using data science tools.In this conversation, he also tells about his own sectoral experiences.

## **Questions**

**1)**Do the forecasting techniques we learn in classes literally work in real life?

**2)** Which of the following is not one of the decision-making processes in traditional/deep learning methods?

a)Interpretability

b)Ability to Direct

c)Ability to Reproduce

d)Being Able to Robust

e)Ability to Translate into a Decision

## (b)

In the second part of the assignment, I have completed some tasks:

• Import the “polls_us_election_2016” data set from the dslabs package.

```{r chunk_1}
library(dslabs)
data("polls_us_election_2016")
```

• Display the first 10 rows of the data set.

```{r chunk_2}
first_ten_row <- head(polls_us_election_2016,10)
print(first_ten_row)
```

• Calculate and display the total number of NA values in the entire data set.

```{r}
total_na <- sum(is.na(polls_us_election_2016))
total_na
```

• Replace all NA values in the “polls_us_election_2016” data set as follows: For
numeric columns, replace NA values with your birth year. For character or factor
columns, replace NA values with your first name. Store the modified data set as
a new object.Print the first ten rows of the new data frame.

```{r}
birth_year<-2002
first_name<-"Yazel"
no_nas_data<-polls_us_election_2016
for (col in names(no_nas_data)){ #Check the type of column
  if (is.numeric(no_nas_data[[col]])) { #If it is a numeric column, replace the NA with the birth year
    no_nas_data[[col]] <- ifelse(is.na(no_nas_data[[col]]), birth_year, no_nas_data[[col]])
  } else { #If it is a character or factor column, replace the NAS with first name
    no_nas_data[[col]] <- ifelse(is.na(no_nas_data[[col]]), first_name, no_nas_data[[col]])
  }
}
new_first_ten_row <- head(no_nas_data,10)
new_first_ten_row 
#[^1]
#[^1]:I wrote this code with the help of ChatGPT.
```

• Print the total number of NAs remaining in the new data frame.

```{r}
total_na<-sum(is.na(no_nas_data))
total_na
```
